1. The table below shows the data about shoe size and height. Create a data frame.
```{r}
shoe_size <- c(6.5, 9.0, 8.5, 8.5, 10.5, 7.0, 9.5, 9.0, 13.0, 7.5, 10.5, 8.5, 12.0, 10.5, 13.0, 11.5, 8.5, 5.0, 10.0, 6.5, 7.5, 8.5, 10.5, 8.5, 10.5, 11.0, 9.0, 13.0)
height <-  c(66.0, 68.0, 64.5, 65.0, 70.0, 64.0, 70.0, 71.0, 72.0, 64.0, 74.5, 67.0, 71.0, 71.0, 77.0, 72.0, 59.0, 62.0, 72.0, 66.0, 64.0, 67.0, 73.0, 69.0, 72.0, 70.0, 69.0, 70.0)
gender <- c("F", "F", "F", "F", "M", "F", "F", "F", "M", "F", "M", "F", "M", "M", "M", "M", "F", "F", "M", "F", "F", "M", "M", "F", "M", "M", "M", "M")

frame1 <- data.frame(Shoesize = shoe_size, Height = height, Gender = gender)
frame1
```
b. Create a subset by males and females with their corresponding shoe size and height.
What its result? Show the R scripts.
```{r}
female <- subset(frame1, Gender == "F", select = c(Shoesize, Height))
female

male <- subset(frame1, Gender == "M", select = c(Shoesize, Height))
male
```
c. Find the mean of shoe size and height of the respondents. Write the R scripts and its result.
```{r}
meanshoe <- mean(frame1$Shoesize)
meanshoe

meanheight <- mean(frame1$Height)
meanheight
```
d. Is there a relationship between shoe size and height? Why?
```{r}
relation <- cor(frame1$Shoesize, frame1$Height)
relation
```
2. Construct character vector months to a factor with factor() and assign the result to factor_months_vector. Print out factor_months_vector and assert that R prints out the factor levels below the actual values.
```{r}
months <- c("March", "April", "January", "November", "January", "September", "October", "September", "November", "August", "January", "November", "November", "February", "May", "August", "July", "December", "August", "August", "September", "November", "February", "April")

fmonths <- factor(months)
fmonths
```
3. Then check the summary() of the months_vector and factor_months_vector. Interpret the results of both vectors. Are they both equally useful in this case?
```{r}
smonths <- summary(months)
sfmonths <- summary(fmonths)

sfmonths
smonths
```
4. Create a vector and factor for the table below.
```{r}
factor_data <- c(rep("East", 1), rep("West", 4), rep("North", 3))
new_order_data <- factor(factor_data, levels = c("East", "West", "North"))

new_order_data
```
5. Enter the data below in Excel with file name = import_march.csv
```{r}

```