1. The table below shows the data about shoe size and height. Create a data frame.
```{r}
shoe_size <- c(6.5, 9.0, 8.5, 8.5, 10.5, 7.0, 9.5, 9.0, 13.0, 7.5, 10.5, 8.5, 12.0, 10.5, 13.0, 11.5, 8.5, 5.0, 10.0, 6.5, 7.5, 8.5, 10.5, 8.5, 10.5, 11.0, 9.0, 13.0)
height <-  c(66.0, 68.0, 64.5, 65.0, 70.0, 64.0, 70.0, 71.0, 72.0, 64.0, 74.5, 67.0, 71.0, 71.0, 77.0, 72.0, 59.0, 62.0, 72.0, 66.0, 64.0, 67.0, 73.0, 69.0, 72.0, 70.0, 69.0, 70.0)
gender <- c("F", "F", "F", "F", "M", "F", "F", "F", "M", "F", "M", "F", "M", "M", "M", "M", "F", "F", "M", "F", "F", "M", "M", "F", "M", "M", "M", "M")

frame1 <- data.frame(Shoesize = shoe_size, Height = height, Gender = gender)
frame1
```
b. Create a subset by males and females with their corresponding shoe size and height.
What its result? Show the R scripts.
```{r}
female <- subset(frame1, Gender == "F", select = c(Shoesize, Height))
female

male <- subset(frame1, Gender == "M", select = c(Shoesize, Height))
male
```
c. Find the mean of shoe size and height of the respondents. Write the R scripts and its result.
```{r}
meanshoe <- mean(frame1$Shoesize)
meanshoe

meanheight <- mean(frame1$Height)
meanheight
```
d. Is there a relationship between shoe size and height? Why?
```{r}
relation <- cor(frame1$Shoesize, frame1$Height)
relation
```
2. Construct character vector months to a factor with factor() and assign the result to factor_months_vector. Print out factor_months_vector and assert that R prints out the factor levels below the actual values.
```{r}
months <- c("March", "April", "January", "November", "January", "September", "October", "September", "November", "August", "January", "November", "November", "February", "May", "August", "July", "December", "August", "August", "September", "November", "February", "April")

fmonths <- factor(months)
fmonths
```
3. Then check the summary() of the months_vector and factor_months_vector. Interpret the results of both vectors. Are they both equally useful in this case?
```{r}
smonths <- summary(months)
sfmonths <- summary(fmonths)

sfmonths
smonths
```
4. Create a vector and factor for the table below.
```{r}
factor_data <- c(rep("East", 1), rep("West", 4), rep("North", 3))
new_order_data <- factor(factor_data, levels = c("East", "West", "North"))

new_order_data
```
5. Enter the data below in Excel with file name = import_march.csv
a. Import the excel file into the Environment Pane using read.table() function. Write the code.
b. View the dataset. Write the R scripts and its result.
```{r}
data <- read.table("import_march.csv", header = TRUE, sep = ",")
data
```
a. Create an R Program that allows the User to randomly select numbers from 1 to 50.
Then display the chosen number. If the number is beyond the range of the selected choice,
it will have to display a string “The number selected is beyond the range of 1 to 50”. If
number 20 is inputted by the User, it will have to display “TRUE”, otherwise display the
input number.
```{r}
exhaustive_search <- function() {
  chosen_number <- as.integer(readline(prompt = "Select a number between 1 and 50: "))
  
  if (is.na(chosen_number)) {
    cat("Please enter a valid number.\n")
    return()
  }
  
  cat("You selected:", chosen_number, "\n")
  
  if (chosen_number < 1 || chosen_number > 50) {
    cat("The number selected is beyond the range of 1 to 50.\n")
  } else if (chosen_number == 20) {
    cat("TRUE\n")
  } else {
    cat(chosen_number)
  }
}

exhaustive_search()


```
a. Write a function that prints the minimum number of bills that must be paid, given the
price of the snack.
Input: Price of snack (a random number divisible by 50) Output: Minimum number of bills
needed to purchase a snack.
```{r}
min_bills <- function(price) {
  bills <- c(1000, 500, 200, 100, 50)
  count <- 0
  
  for (bill in bills) {
    num_bills <- price %/% bill
    count <- count + num_bills
    price <- price %% bill
  }
  
  return(count)
}

snack_price <- as.numeric(readline(prompt = "Enter the price of the snack (divisible by 50): "))
if (snack_price %% 50 == 0) {
  cat("Minimum number of bills needed:", min_bills(snack_price), "\n")
} else {
  cat("Price must be a number divisible by 50.\n")
}

```